### 2023-09-02 sections/4-results.tex
update hw specs

Ark: a 28-core Intel Xeon E5-2690 v4 2.60GHz, 512GB RAM and CentOS 7 Linux with kernel 5.15.50-1-MANJARO \#1 SMP PREEMPT. Rust 1.62, Python 3.10.5

Macbook Air: 8-core (4 performance, 4 efficiency) Apple M1 processor with 16GB RAM, macOS 12.1. Rust 1.62, Python 3.9.4

>>>>

Ark: a 28-core Intel Xeon E5-2690 v4 2.60GHz, 512GB RAM, Manjaro Linux with kernel 5.15.78-1-MANJARO \#1 SMP PREEMPT. Rust 1.70, Python 3.10.5

Macbook Air: 8-core (4 performance, 4 efficiency) Apple M1 processor with 16GB RAM, macOS 12.1. Rust 1.70, Python 3.9.4

Amazon AWS: 64-core Intel Xeon Platinum 8375C CPU 2.90GHz, 512GB RAM, Ubuntu 22.04.3-Ubuntu SMP. Rust 1.71.1, Python 3.10.12
